\section{Experimental Setup}

\subsection{Hardware}
The detector is made up of layers of scintillators. These are read out by a photomultiplier and energy absorbing metal plates. Between the first and the second scintillator layer there is a 2.5 cm thick iron plate, between the others there are 8 cm thick aluminium plates.

\subsubsection{Scintillation detector}
A scintillation detector consists of a scintillator and a photomultiplier. When the scintillator is hit by a (charged) particle it absorbs its energy and emits it in the form of electromagnetic radiation, mostly visible or UV light.  To be able to detect how much energy is being absorbed the light reaches a photomultiplier. Due of the photoelectric effect materials emit electrons when light with a certain frequency hits the material. These electrons are then focused and an electric pulse can be measured and analysed. This in turn gives information about the original particle that struck the scintillator. 

\subsection{Expected energy loss in the detector}
Using the simple model, that the muons are roughly minimum ionizing particles (MIPS), which is reasonable in the range of expected muon energies (average of 2 GeV \ref{manual}), and therefore loose around 2 MeV$\frac{\text{cm}^2}{\text{g}}$, we can calculate the average energy loss for the muons in the detector (Fig.\,\ref{f:bethebloch}). In the iron plate they loose $\approx$ 39 MeV and in the three aluminium plates they loose $\approx$ 130 MeV. Assuming that there is roughly 1 m of concrete above the experiment they will approximately loose an additional 400 MeV there. In total the muons will on average loose less than 600 MeV of energy. Knowing that the average energy of the muons is 2 GeV, one would expect most muons to just pass the whole detector. 

\input{relativerates.tex}

